Differentially Private Bayesian Inference

### 2018-07-07 main.tex
note organization updates

\section{Experimental Evaluations}
\subsection{Computation Efficiency}
The formula for computing the local sensitivity presented in Sec. \ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property. i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$. We also have some experiments for validating our proposal as in Fig. \ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$. It is shown that maximum value taken when  $r = \bysinfer(x)$.

\subsection{Experimental Evaluations on Accuracy}
In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kinds of sensitivity and the Laplace mechanism.

\subsubsection{Based on Hellinger Distance}
\label{subsec_accuracy_hellinger}
% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
% \caption{The experimental results of accuracy of four algorithms}
% \label{fig_data}
% \end{center}
% \end{figure*}

So we need to have a further exploration on the accuracy trade-off between Laplace mechanism and our exponential mechanism.

\subsubsection{Based on $L_1$ Norm}
\label{subsec_accuracy_l1}
In this section, we will study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig. \ref{fig_dirichlet_hellinger_l1}.

\subsection{Evaluations on Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
\label{subsec_accuracy_tradeoff}
Based on accuracy study in Sec. \ref{subsec_accuracy_hellinger} and \ref{subsec_accuracy_l1}, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism. We will do analysis both in theory and experiment and do some concrete case studies.

\subsubsection{Theory Analysis}
In this part, we will do theory analysis on the two mechanisms' discrete probabilities of outputting each candidate separately. In following analysis, we will count the probabilities wrt. the steps from correct answer, in order to be more concise and comparable to the experiment results from Sec. \ref{subsec_accuracy_hellinger}. For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$. Under the Hellinger distance measurement, if candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer. i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$. This will make the results more clear and observable.

@@

	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set. In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are i.i.d. So we will have a list of noise $L_{noise} = \{|Lap_1|, |Lap_2|,\cdots ,|Lap_{m-1}|\}$ by taking the absolute value of each noise $|Lap_i|$. In order to get the probability of a single candidate, we also need to have the set of noises $S_{noise}$ obtained from $L_{noise}$ by removing its duplicate values and the list $L_{noise/0}$ by removing 0s from $L_{noise}$. Then, the probabilities of outputting a single candidate in Laplace mechanism can be obtained by:

	\begin{equation*}
	\begin{split}
	Pr[(Lap_1, Lap_2, \cdots, Lap_{m-1})]  
	& = \frac{1}{|S_{noise}|! \times 2^{|L_{noise/0}|}} \times Pr[(|Lap_1|, |Lap_2|, \cdots, |Lap_{m-1}|)] \\
	& = \frac{1}{|S_{noise}|! \times 2^{|L_{noise/0}|}} \times Pr[|Lap_1| \leq Lap(\frac{2}{\epsilon}) < |Lap_1| + 1] \\
	& \times Pr[|Lap_2| \leq Lap(\frac{2}{\epsilon}) < |Lap_2| + 1] \times \cdots \\
	& \times Pr[|Lap_{m-1}| \leq Lap(\frac{2}{\epsilon}) < |Lap_{m-1}| + 1]
	\end{split}
	\end{equation*}

	By summing up the probability value of candidates whose steps from correct answer are the same, we can finally get the probability wrt. steps from correct answer in Laplace mechanism.

	From analysis above, we can see the probabilities of outputting the good answers will not change a lot as the size of the candidate set increasing. Specifically, we can easily have two upper bounds: $|S_{noise}| \leq (m-1)$ and $|L_{noise/0}| \leq (m-1)$. From the two upper bounds, we can see that the probabilities of outputting good answers are decreasing with speed upper bounded by $(m-1)! \times 2^{m-1}$. Since $n \gg 2$ and $m$ is usually smaller than $10$, it is easy to see that the decay speed $(m-1)! \times 2^{m-1}$ in Laplace mechanism is much more smaller than $n^{m-1}$ in our exponential mechanism. Moreover, when the steps are small, $0$ for example, $|S_{noise}| = |L_{noise/0}|  = 0$, which means the probability of correct answer will decrease very little no matter how large the candidate set is.

@@

		\item when the prior is $\dirichlet(1,1,1)$, the observed data set $x = (20,20,20)$ (suppose a black box will produce $A$, $B$, $C$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$, $20$ times $B$ and $20$ times $C$), we can get the posterior distribution $\dirichlet(21,21,21)$

@@

		In this case, it is hard to tell which one is better because Laplace mechanism can output some good answers (for example, the correct answer) better than our mechanism but cannot go better with other good answers.

		\item when the prior is $\dirichlet(1,1,1,1)$, the observed data set is $(1,1,1,50)$ (the same meaning as above), we can get the posterior distribution $\dirichlet(2,2,2,51)$. Some probabilities from the two mechanisms are listed as follows:
		\begin{center}
		 \begin{tabular}{c | c | c} 
		 \hline
		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		 \hline\hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.999999999998] / \cdots 	$ & 0.000213865923868 & 6.16388940464e-11\\ 
		 \hline
		 \multicolumn{3}{c}{$\cdots$}  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.340503311163] / 2		$ & 0.000388935212208 & 0.0360289071389 \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.249722620018 ] / 1		$ & 0.000464587461035 & 0.0360289071389  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.000252512987228 & 0.0358325423325 \\
		 \hline
		\end{tabular}
		\end{center}

@@

@@

\subsubsection{Experiment Analysis}
In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism. By computing the two mechanisms' discrete probabilities wrt. steps (i.e., Hellinegr distance) from correct answer under different settings, we got groups of results as in Fig. \ref{fig_theory_50_50}, \ref{fig_theory_20_20_20}, \ref{fig_theory_20_20_20_20} and \ref{fig_theory_1_1_1_77}.

Subfigs (a) based on Sec. \ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times. The x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance. Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt. the steps. The x-axis is the Hellinger distance from correct answer, i.e. steps from correct answer. Since they have the same meaning, we just use the Hellinger distance to label the x-axis here. The y-axis is the probability of output candidates with corresponding steps (i.e. Hellinger distance) from correct answer.

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
  \subfigure[discrete probabilities wrt. hellinger distance]{
    \includegraphics[width=0.48\textwidth]{50_50.eps}} 
\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
\label{fig_theory_50_50}
\end{center}
\end{figure*}

When the data size and the dimension of the prior distribution is small, our exponential mechanism can do better than Laplace, both in experiments and in theory, as shown in Fig. \ref{fig_theory_50_50}. In Subfig. \ref{fig_theory_50_50}(a), the experiment results show that the average Hellinger distance of our mechanism's outputs are smaller than Laplace mechanism, i.e., the average accuracy of our mechanism is higher than Laplace mechanism. In the mean time, the theory calculation results in Subfig. \ref{fig_theory_50_50}(b) also show that our exponential mechanism can output good answers with higher probabilities and output bad answers with lower probabilities than Laplace mechanism.

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
  \subfigure[discrete probabilities wrt. hellinger distance]{
    \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20)$, $\epsilon = 0.8$ and $\delta = 0.000005$}
\label{fig_theory_20_20_20}
\end{center}
\end{figure*}

In Fig. \ref{fig_theory_20_20_20}, we plotted the results under the case ($x = (20,20,20)$). SubFig. \ref{fig_theory_20_20_20}(a) shows that the average accuracy of Laplace mechanism is slightly better than our mechanism. Meanwhile, the SubFig. \ref{fig_theory_20_20_20}(b) shows the Laplace mechanism have higher probabilities on some good answers but lower on some other good answers. The advantage is not significant. So, we increase the data size and the dimension in next case to have a further study.

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
  \subfigure[discrete probabilities wrt. hellinger distance]{
    \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
\label{fig_theory_20_20_20_20}
\end{center}
\end{figure*}

Here we studied the case when data size $n = 80$ and observed data set $x=(20,20,20,20)$ and plotted these discrete probabilities, shown in Fig. \ref{fig_theory_20_20_20_20}.  Subfig. \ref{fig_theory_20_20_20_20}(a) shows that the Laplace mechanism is better than our exponential mechanism very obviously. Subfig \ref{fig_theory_20_20_20_20}(b) shows that the Laplace can output most of the good answers with higher probabilities than our exponential mechanism. The advantage in the SubFig. \ref{fig_theory_20_20_20_20}(a) is obvious but still not significant in SubFig. \ref{fig_theory_20_20_20_20}(b). So, we change the variance of the observed data set in the next case.

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.48\textwidth]{theory_compare_1_1_1_77.eps}}
  \subfigure[discrete probabilities wrt. hellinger distance]{
    \includegraphics[width=0.48\textwidth]{1_1_1_77.eps}} 
\caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (1,1,1,77) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
\label{fig_theory_1_1_1_77}
\end{center}
\end{figure*}

In Fig. \ref{fig_theory_1_1_1_77}, we considered an edge case where the variance of the observed data set is small: $x=(1,1,1,77)$ and plotted these discrete probabilities. This plot can show clearly that the Laplace mechanism is much better than our exponential mechanism, both in (a) and (b). In Subfig. \ref{fig_theory_1_1_1_77}(b), the average accuracy of Laplace mechanism is conspicuously better than the other three exponential mechanisms. Also, in Subfig. \ref{fig_theory_1_1_1_77}(b), the Laplace mechanism can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously. Moreover, no matter good answers or bad answers, their outputting probabilities are very close in our exponential mechanism.

From the theory and experimental analysis above, we obtained some conclusions
\begin{enumerate}
	\item when the data size and the dimensions of the prior distribution are small (candidate set size $n^{m-1}$ around 5000, our exponential mechanism with smooth sensitivity can do better than Laplace mechanism.

	\item when the observed data set is close to center (i.e., the variance is large), the performance of the two mechanisms are close to each other.

	\item The Laplace mechanism will beat us when the data size and the dimensions of the prior distribution increasing and when the variance of the observed data set is small.
\end{enumerate}

\subsection{Accuracy Evaluation wrt. Different Variables}
\label{subsubsec_vs_variables}

>>>>

\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
\label{subsec_accuracy_tradeoff}
Based on accuracy study above, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism in four aspects: data size, dimensions, prior distribution and data variance.

\subsubsection{Accuracy Analysis wrt. Data Size and Distribution Dimensions}
In this part, we will analyze the influence of data size on the two mechanisms' discrete probabilities of outputting each candidate separately. In following analysis, we will count the probabilities wrt. the steps from correct answer, in order to be more concise and comparable to the experiment results from Sec. \ref{subsec_accuracy_hellinger}. For example, in the case where the correct posterior distribution is $\betad(5,5)$, the candidate $\betad(4,6)$ and $\betad(6,4)$ are of $1$ steps from $\betad(5,5)$; when correct posterior distribution is $\dirichlet(5,5,5)$, the candidate $\dirichlet(4,5,3)$, $\dirichlet(4,3,5)$, $\dirichlet(5,4,3)$, $\dirichlet(5,3,4)$, $\dirichlet(3,5,4)$ and $\dirichlet(5,5,5)$ are all of $1$ step from $\dirichlet(5,5,5)$. Under the Hellinger distance measurement, if candidates are of the same steps from correct answer, they also have the same Hellinger distance from correct answer. i.e for every $\hlg(\bysinfer(x), z) = c$, it will have a corresponding steps $step(\hlg(\bysinfer(x), z) = c) = k$. This will make the results more clear and observable.

@@

	\item However in Laplace mechanism, the probability of producing noise has little relevance with the size of the candidate set. In $m$ dimensional Dirichlet distribution, when the correct posterior distribution is $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$, we are adding Laplace noise in this way: $\dirichlet(\alpha_1 + Lap_1, \alpha_2 + Lap_2, \cdots, n - (\alpha_1 + Lap_1 + \alpha_{m-1} + Lap_{m-1}))$ where $Lap_i \sim Floor(Lap(\frac{2}{\epsilon}))$ are i.i.d. So, the probabilities of outputting a single candidate in Laplace mechanism can be obtained by:

	\begin{equation*}
	\begin{split}
	Pr[(Lap_1, Lap_2, \cdots, Lap_{m-1})]  
	& = Pr[Lap_1 \leq Lap(\frac{2}{\epsilon}) < Lap_1 + 1] \\
	& \times Pr[Lap_2 \leq Lap(\frac{2}{\epsilon}) < Lap_2 + 1] \times \cdots \\
	& \times Pr[Lap_{m-1} \leq Lap(\frac{2}{\epsilon}) < Lap_{m-1} + 1],
	\end{split}
	\end{equation*}
	where $Pr[Lap_i \leq Lap(\frac{2}{\epsilon}) < Lap_i + 1] = \frac{1}{2} Pr[|Lap_i| \leq Lap(\frac{2}{\epsilon}) < |Lap_i| + 1]$ when $Lap_i > 0$ and $\frac{1}{2} Pr[|Lap_i| - 1 \leq Lap(\frac{2}{\epsilon}) < |Lap_i|]$ else.

	From analysis above, we can see the probabilities of outputting the good answers will not change a lot as the size of the candidate set increasing. Specifically, we can see that the probabilities of outputting good answers are decreasing with speed upper bounded by , which means the probability of correct answer will decrease very little no matter how large the candidate set is.

@@

		\item keep the prior unchanged, $\betad(1,1,1)$, the observed data set $x = (20,20)$ (suppose a black box will produce $A$, $B$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$ and $20$ times $B$, we can get the posterior distribution $\betad(21,21)$

@@

@@

		% In this case, it is hard to tell which one is better because Laplace mechanism can output some good answers (for example, the correct answer) better than our mechanism but cannot go better with other good answers.

		% \item when the prior is $\dirichlet(1,1,1,1)$, the observed data set is $(1,1,1,50)$ (the same meaning as above), we can get the posterior distribution $\dirichlet(2,2,2,51)$. Some probabilities from the two mechanisms are listed as follows:
		% \begin{center}
		%  \begin{tabular}{c | c | c} 
		%  \hline
		%  Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		%  \hline\hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.999999999998] / \cdots 	$ & 0.000213865923868 & 6.16388940464e-11\\ 
		%  \hline
		%  \multicolumn{3}{c}{$\cdots$}  \\
		%  \hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.340503311163] / 2		$ & 0.000388935212208 & 0.0360289071389 \\
		%  \hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.249722620018 ] / 1		$ & 0.000464587461035 & 0.0360289071389  \\
		%  \hline
		%  $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.000252512987228 & 0.0358325423325 \\
		%  \hline
		% \end{tabular}
		% \end{center}

		% This case shows that the Laplace mechanism do much better than our exponential mechanism significantly. These good answers with few steps from correct answer can be outputted with higher probabilities in Laplace mechanism than in our mechanism. Moreover, in our mechanism the bad answers and good answers have very similar outputting probabilities.

@@

\subsubsection{Accuracy Analysis wrt. prior distribution}

\subsubsection{Accuracy Analysis wrt. data variance}

\section{Experimental Evaluations}
\label{experiment}

\subsection{Computation Efficiency}
\label{subsec_effi}
The formula for computing the local sensitivity presented in Sec. \ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property. i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$. We also have some experiments for validating our proposal as in Fig. \ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$. It is shown that maximum value taken when  $r = \bysinfer(x)$.

\subsection{Experimental Evaluations on Accuracy}
\label{subsec_experiment_accuracy}

In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kinds of sensitivity and the Laplace mechanism.
% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
% \caption{The experimental results of accuracy of four algorithms}
% \label{fig_data}
% \end{center}
% \end{figure*}

Then, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig. \ref{fig_dirichlet_hellinger_l1}.

In consequence, we have a further experiments exploration on the accuracy trade-off between Laplace mechanism and our exponential mechanism in next section.

% \subsubsection{Experiment Analysis}
% In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism. By computing the two mechanisms' discrete probabilities wrt. steps (i.e., Hellinegr distance) from correct answer under different settings, we got groups of results as in Fig. \ref{fig_theory_50_50}, \ref{fig_theory_20_20_20}, \ref{fig_theory_20_20_20_20} and \ref{fig_theory_1_1_1_77}.

% Subfigs (a) based on Sec. \ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times. The x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance. Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt. the steps. The x-axis is the Hellinger distance from correct answer, i.e. steps from correct answer. Since they have the same meaning, we just use the Hellinger distance to label the x-axis here. The y-axis is the probability of output candidates with corresponding steps (i.e. Hellinger distance) from correct answer.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{50_50.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_50_50}
% \end{center}
% \end{figure*}

% When the data size and the dimension of the prior distribution is small, our exponential mechanism can do better than Laplace, both in experiments and in theory, as shown in Fig. \ref{fig_theory_50_50}. In Subfig. \ref{fig_theory_50_50}(a), the experiment results show that the average Hellinger distance of our mechanism's outputs are smaller than Laplace mechanism, i.e., the average accuracy of our mechanism is higher than Laplace mechanism. In the mean time, the theory calculation results in Subfig. \ref{fig_theory_50_50}(b) also show that our exponential mechanism can output good answers with higher probabilities and output bad answers with lower probabilities than Laplace mechanism.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20)$, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_20_20_20}
% \end{center}
% \end{figure*}

% In Fig. \ref{fig_theory_20_20_20}, we plotted the results under the case ($x = (20,20,20)$). SubFig. \ref{fig_theory_20_20_20}(a) shows that the average accuracy of Laplace mechanism is slightly better than our mechanism. Meanwhile, the SubFig. \ref{fig_theory_20_20_20}(b) shows the Laplace mechanism have higher probabilities on some good answers but lower on some other good answers. The advantage is not significant. So, we increase the data size and the dimension in next case to have a further study.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_20_20_20_20}
% \end{center}
% \end{figure*}

% Here we studied the case when data size $n = 80$ and observed data set $x=(20,20,20,20)$ and plotted these discrete probabilities, shown in Fig. \ref{fig_theory_20_20_20_20}.  Subfig. \ref{fig_theory_20_20_20_20}(a) shows that the Laplace mechanism is better than our exponential mechanism very obviously. Subfig \ref{fig_theory_20_20_20_20}(b) shows that the Laplace can output most of the good answers with higher probabilities than our exponential mechanism. The advantage in the SubFig. \ref{fig_theory_20_20_20_20}(a) is obvious but still not significant in SubFig. \ref{fig_theory_20_20_20_20}(b). So, we change the variance of the observed data set in the next case.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_1_1_1_77.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{1_1_1_77.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (1,1,1,77) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_1_1_1_77}
% \end{center}
% \end{figure*}

% In Fig. \ref{fig_theory_1_1_1_77}, we considered an edge case where the variance of the observed data set is small: $x=(1,1,1,77)$ and plotted these discrete probabilities. This plot can show clearly that the Laplace mechanism is much better than our exponential mechanism, both in (a) and (b). In Subfig. \ref{fig_theory_1_1_1_77}(b), the average accuracy of Laplace mechanism is conspicuously better than the other three exponential mechanisms. Also, in Subfig. \ref{fig_theory_1_1_1_77}(b), the Laplace mechanism can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously. Moreover, no matter good answers or bad answers, their outputting probabilities are very close in our exponential mechanism.

% From the theory and experimental analysis above, we obtained some conclusions
% \begin{enumerate}
% 	\item when the data size and the dimensions of the prior distribution are small (candidate set size $n^{m-1}$ around 5000, our exponential mechanism with smooth sensitivity can do better than Laplace mechanism.

% 	\item when the observed data set is close to center (i.e., the variance is large), the performance of the two mechanisms are close to each other.

% 	\item The Laplace mechanism will beat us when the data size and the dimensions of the prior distribution increasing and when the variance of the observed data set is small.
% \end{enumerate}

\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
\label{subsubsec_vs_variables}
